---
title: "Multiple Factors"
author: "Chase Clark"
date: "January 17, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Load dendrogram cached file for testing with:
```{r}
library("tidyverse")
library("dendextend")

dend<-readRDS("Data/Distance-cosineD_Clustering-ward.D2_UsedPresenceAbsence_SNR-4_PercentPresence-70_LowCut-3000_HighCut-15000.rds")

# dend<-dend %>% set("labels_color", "white")

dend<-dend %>% set("labels_cex", .65)

```

Read csv of groups
```{r}
groupFile<-read_csv("data/b.csv")
```

Load colored_Dots.R function
```{r,include=FALSE}
source('~/Documents/GitHub/DendrogramAndDots/R/colored_Dots.R', echo=TRUE)
```



```{r}

dendrogramLabels<-as_tibble(labels(dend))
names(dendrogramLabels)<-'Sample name'

#join but keep prder of dendrogram label
joinedData<-left_join(dendrogramLabels,groupFile,by="Sample name")

naReplaceValues<-as.list(sapply(names(joinedData),function(x)paste0("Missing ",x)))

joinedData<-joinedData %>%  replace_na(replace=naReplaceValues)



```

```{r}
biggerList<-NULL
for (i in 1:4){
  
aw<-names(joinedData)[3:6]
colsel<-aw[i]

small<-bind_cols(joinedData[,1],joinedData[colsel])

groupedList<-split(small,factor(small[colsel][[1]]))

bigList<-lapply(1:length(groupedList),function(x)left_join(dendrogramLabels,groupedList[[x]],by='Sample name'))

labels(bigList)<-labels(groupedList)



for(x in 1:length(bigList)){
    bigList[[x]][colsel][!is.na(bigList[[x]][colsel])]<-"#000000"
    bigList[[x]][colsel][is.na(bigList[[x]][colsel])]<-"#00000000"
}

bigList<-list(bigList)
biggerList<-c(biggerList,bigList)
}

```



```{r}
a<-which(bigList$Marine_water$Sample_type_2 == "#000000")
b<-joinedData[a,]
```


```{r}
biggerListunlisted<-unlist(biggerList,recursive = F)
```


```{r}
b<-biggerListunlisted
c <- b %>% map(as.data.frame)
c %>% reduce(., merge, by = 2, all = TRUE)
d<-c %>% reduce( merge, by = "Sample name", all = TRUE)
names(d)<-c("Sample_ID",names(c))
```





Now we we have a list. Each list item represents a group/column from excel table.
These are associated to the entire dendrogram, by label and are in the same order as the dendrogram from top to bottom.
0 means a label is not part of the group, 1 means it is part of the group


/#000000  is black
/#00000000 is black but transparent   in case we want color supprt later



```{r}
bigMatrix<-NULL
for (i in 1:length(bigList)){
    bigMatrix<-bind_cols(bigMatrix,bigList[[i]][,2])}

names(bigMatrix)<-names(bigList)

```



The below chunk will only run when the rmd file is run with R (won't work if viewing static html).








```{r,fig.height=175}

    par(mar = c(8,3,8,25))

    plot(dend,horiz=T)
    
    colored_dots(bigMatrix, dend,
         rowLabels = names(bigMatrix),horiz=T,sort_by_labels_order = FALSE) 

    
    
  
  
```
